### 2020-12-22 paper/localpsf.tex
editing construction section

%		\Return{$\mu$, $\Sigma$}
	}
	\caption{Compute volume $\alpha_h$, mean $\mu_h$, and covariance $\Sigma_h$}
	\label{alg:varhpi_mean_cov}
\end{algorithm2e}

@@

Ideally, sample points $x_i$ and $x_j$ should be far enough apart from each other that the supports of $\left\langle\mathcal{A}, \delta_{x_i}\right\rangle^*$ and $\left\langle\mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap.

@@

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ from $P$, one at a time. The current candidate point, $p$, is the point in $P$ that is the farthest away from all points in previous sample point baches. That is, the maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
After we choose the candidate $p$, we remove $p$ from $P$.
If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until there are no more points in $P$. 
%This is detailed in Algorithm \ref{alg:point_choice}.

We repeat the process to construct several batches of points $S_1, S_2, \dots$, until the total number of sample points exceeds a desired threshold. In our implementation, the set of candidate points $P$ is the set of all Lagrange nodes for the finite element basis functions used to discretize the problem, minus all points in previously chosen batches.

>>>>

%		\Return{$\mu$, $\Sigma$}
	}
	\caption{Compute volume $\alpha$, mean $\mu$, and covariance $\Sigma$}
	\label{alg:varhpi_mean_cov}
\end{algorithm2e}

@@

% sample points $x_i$ and $x_j$ should be far enough apart from each other that the supports of $\left\langle\mathcal{A}, \delta_{x_i}\right\rangle^*$ and $\left\langle\mathcal{A}, \delta_{x_j}\right\rangle^*$ do not overlap.

@@

Starting from a finite set of candidate points $P$, we select batches of sample points, $S_b$, using a greedy algorithm. To build a batch $S_b$, first we initialize $S_b$ as an empty set. Then we select a candidate point $p \in P$ that is the farthest away from all points in previous sample point batches. That is, the maximizer of the following optimization problem:
\begin{equation*}
\max_{p \in P} \min_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|.
\end{equation*}
Once $p$ is selected, we remove $p$ from $P$. If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until there are no more points in $P$.  This is detailed in Algorithm \ref{alg:point_choice}.

%We select a batches of sample points, $S_b$, from a finite set of candidate points $P$ using a greedy algorithm. Starting from an empty set, we build $S_b$ from candidate points $p$ from $P$, one point at a time. The current candidate point, $p$, is the point in $P$

We repeat the process to construct several batches of points $S_1, S_2, \dots$, until the number of batches exceeds a desired threshold. In our implementation, the set of candidate points $P$ is initialized as the set of all Lagrange nodes for the finite element basis functions used to discretize the problem, minus all points in previously chosen batches. The set $P$ is re-initialized for each batch $S_b$.
